Thesis outline

### 2017-06-17 KellyDouglass/Thesis/Thesis_sections/Conclusion.tex
Added acknowledgments and dedication

We find that the large-scale environment influences the chemical evolution of 
dwarf galaxies by estimating the gas-phase oxygen (O/H) and nitrogen (N/H) 
abundances and the N/O ratio of star-forming dwarf galaxies in SDSS DR7 using 
the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
in the MPA-JHU catalog \citep[Douglass et al., 2017, in prep]{Douglass17a,
Douglass17b}.  Due to the minimum redshift limit for detecting the [\ion{O}{2}] 
$\lambda$3727 emission line in SDSS DR7 spectra, only 135 star-forming dwarf 
galaxies are available for analysis with the Direct $T_e$ method.  With this 
sample, we see no difference in the metallicity (O/H) between dwarf galaxies in 
voids and denser regions \citep{Douglass17a}.  Upon closer inspection, we find 
minor shifts in the distributions of gas-phase chemical abundances for void 
dwarf galaxies when compared to dwarf galaxies in denser regions: star-forming 
void dwarf galaxies have higher oxygen abundances (O/H), lower nitrogen 
abundances (N/H), and lower N/O ratios \citep{Douglass17b}.

>>>>

We find that the large-scale environment influences the chemical evolution of 
dwarf galaxies by estimating the gas-phase oxygen (O/H) and nitrogen (N/H) 
abundances and the N/O ratio of star-forming dwarf galaxies in SDSS DR7 using 
the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
in the MPA-JHU catalog \citep[Douglass et al., 2017, submitted]{Douglass17a,
Douglass17b}.  Due to the minimum redshift limit for detecting the [\ion{O}{2}] 
$\lambda$3727 emission line in SDSS DR7 spectra, only 135 star-forming dwarf 
galaxies are available for analysis with the Direct $T_e$ method.  With this 
sample, we see no difference in the metallicity (O/H) between dwarf galaxies in 
voids and denser regions \citep{Douglass17a}.  Upon closer inspection, we find 
minor shifts in the distributions of gas-phase chemical abundances for void 
dwarf galaxies when compared to dwarf galaxies in denser regions: star-forming 
void dwarf galaxies have higher oxygen abundances (O/H), lower nitrogen 
abundances (N/H), and lower N/O ratios \citep{Douglass17b}.

### 2017-06-17 KellyDouglass/Thesis/Thesis_sections/GV.tex
Added acknowledgments and dedication

\chapter[Green valley galaxies]{Identifying green valley galaxies}\label{ch:GV}

@@

\section[Theory]{Calculating the color of a galaxy}

@@

\section[Data]{SDSS and GALEX data}

@@

The SDSS Data Release 7 \citep[DR7;][]{Abazajian09} is a wide-field multi-band 
imaging and spectroscopic survey that uses drift scanning to map approximately 
one-quarter of the northern sky.  A dedicated 2.5-meter telescope at the Apache 
Point Observatory in New Mexico takes photometric data in the five-band SDSS 
system --- $u$, $g$, $r$, $i$, and $z$ \citep{Fukugita96,Gunn98}.  Galaxies with 
a Petrosian $r$-band apparent magnitude $m_r < 17.77$ are selected for 
spectroscopic analysis \citep{Lupton01,Strauss02}.  Gas-phase chemical 
abundances are calculated via the Direct $T_e$ method using emission-line fluxes 
measured by the MPA-JHU catalog\footnote{Available at 
\url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in Douglass et al. 
(2017, in prep).  The large-scale environment of the galaxies is based on the 
void catalog compiled by \cite{Pan12}.  This void catalog is constructed from 
SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  Galaxies which are 
located within the identified voids are labeled as void galaxies; those which do 
not reside in a void are designated as wall galaxies.  Because the minimum 
diameter of a void is defined as 10 \hMpc , the large-scale environment of 
galaxies within 5 \hMpc of the edge of the SDSS DR7 footprint cannot be 
described, so their environment is labeled as unknown.

@@

\section[Results]{Classification of galaxies in the color-magnitude diagram}

% CMD in NUV-r, showing where green valley galaxies live
\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/GV/NUVr_CMD_3pop_scatter}
    \caption[NUV-$r$ color-magnitude diagram of SDSS galaxies]{The NUV$-r$ 
    color-magnitude diagram of galaxies in SDSS DR7.  Those galaxies in the red 
    contours have morphological classifications of either normal early types 
    (aimc $=1$) or blue early types (aimc $=2$), as determined by the KIAS-VAGC.  
    The green points represent a subset of the normal late type galaxies (aimc 
    less than 25, excluding those with values of 1 or 2), and the blue contours 
    represents the remaining normal late type galaxies (aimc greater than 25).  
    It is clear that this morphological classification defines those galaxies 
    that are transitioning from the blue sequence to the red cloud.}
    \label{fig:NUVr_CMD}
\end{figure}

@@

% Histogram of NUV-r, with all, red, blue, green galaxies (aimc values)
\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/GV/NUVr_CMDclassifications}
    \caption[Distribution of NUV-$r$ of SDSS galaxies]{A histogram of the 
    NUV$-r$ color of those SDSS DR7 galaxies which are also detected in GALEX.  
    The red cloud, blue sequence, and green valley populations are separated by 
    the morphological types as defined by the KIAS-VAGC.  It is readily apparent 
    that the green valley galaxies exist in the space between the red cloud and 
    blue sequence.}
    \label{fig:NUVr_hist}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.65\textwidth]{Images/GV/Mstar_hist}
    \caption[Stellar mass distribution by morphological type]{The distribution 
    of stellar mass for all galaxies in SDSS DR7, separated by their 
    morphological type.  The galaxies in the green valley have stellar masses 
    comparable to those in the red cloud.  The stellar masses of those galaxies 
    in the blue sequence range from the lowest mass objects up through the 
    stellar masses of the green valley galaxies.}
    \label{fig:M_hist}
\end{figure}

@@

Estimates of the gas-phase chemical abundances of galaxies probe their 
integrated star formation histories, which can provide insight into the 
enrichment of the ISM and CGM.  A few of the galaxies for which Douglass et al. 
(2017, in prep) are able to estimate metallicities reside in the green valley.  
When compared with the metallicities of galaxies in the blue sequence and red 
cloud, Fig. \ref{fig:Z_hist} shows that the green valley galaxies have higher 
nitrogen abundances than star-forming galaxies in the blue sequence (and some of 
the red cloud).  With oxygen abundances that fall within the same range as the 
other two galaxy populations, this shift causes the N/O ratio to be much higher 
in green valley galaxies than in the blue sequence.  Our interpretation of this 
shift is described in Sec. \ref{sec:discussion_GV}.

@@

\section[Discussion]{Understanding green valley galaxies}\label{sec:discussion_GV}

@@

Fig. \ref{fig:Mr_bin} shows a higher fraction of faint wall galaxies than faint 
void galaxies are in the green valley.  This would indicate that void galaxies 
are slightly behind wall galaxies in their evolution, matching predictions based 
on the $\Lambda$CDM cosmology.  These results also coincide with the 
observations of \cite{Douglass17b} and Douglass \& Vogeley (2017, in prep).  
They find that, for dwarf galaxies ($M_r > -17$), those which exist in voids may 
have commenced their star formation at a later time.  The higher fraction of 
wall dwarf galaxies in the green valley might also point to an environmental 
influence on the reason for transitioning through the green valley, such as ram 
pressure stripping, which would occur much less frequently in the void 
environment.  However, the existence of void galaxies in the green valley 
indicate that galaxy interactions cannot be the only star formation quenching 
mechanism.

@@

\section[Conclusions]{Conclusions}

@@

There is a higher fraction of faint wall galaxies than faint void galaxies in 
the green valley.  In conjunction with the conclusions of \cite{Douglass17b} and 
Douglass et al. (2017, in prep), this indicates that void dwarf galaxies are 
less evolved than dwarf galaxies in denser environments.  It would be beneficial 
to investigate the small-scale ($\sim$1 \hMpc) environment of galaxies in the 
green valley, to determine if any interactions are responsible for the 
transitional state.

>>>>

\chapter[Green Valley Galaxies]{Identifying Green Valley Galaxies}\label{ch:GV}

@@

\section[Color Calculations]{Calculating the color of a galaxy}

@@

\section[SDSS Data]{SDSS and GALEX data}

@@

The SDSS Data Release 7 \citep[DR7;][]{Abazajian09} is a wide-field multi-band 
imaging and spectroscopic survey that uses drift scanning to map approximately 
one-quarter of the northern sky.  A dedicated 2.5-meter telescope at the Apache 
Point Observatory in New Mexico takes photometric data in the five-band SDSS 
system --- $u$, $g$, $r$, $i$, and $z$ \citep{Fukugita96,Gunn98}.  Galaxies with 
a Petrosian $r$-band apparent magnitude $m_r < 17.77$ are selected for 
spectroscopic analysis \citep{Lupton01,Strauss02}.  Gas-phase chemical 
abundances are calculated via the Direct $T_e$ method using emission-line fluxes 
measured by the MPA-JHU catalog\footnote{Available at 
\url{http://www.mpa-garching.mpg.de/SDSS/DR7}} and published in Douglass et al. 
(2017, submitted).  The large-scale environment of the galaxies is based on the 
void catalog compiled by \cite{Pan12}.  This void catalog is constructed from 
SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  Galaxies which are 
located within the identified voids are labeled as void galaxies; those which do 
not reside in a void are designated as wall galaxies.  Because the minimum 
diameter of a void is defined as 10 \hMpc , the large-scale environment of 
galaxies within 5 \hMpc of the edge of the SDSS DR7 footprint cannot be 
described, so their environment is labeled as unknown.

@@

\section[Classifying the CMD]{Classification of galaxies in the color-magnitude diagram}

% CMD in NUV-r, showing where green valley galaxies live
\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/GV/NUVr_CMD_3pop_scatter}
    \caption[NUV-$r$ color-magnitude diagram of SDSS galaxies]{The NUV$-r$ 
    color-magnitude diagram of galaxies in SDSS DR7.  Those galaxies in the red 
    contours have morphological classifications of either normal early types 
    (aimc $=1$) or blue early types (aimc $=2$), as determined by the KIAS-VAGC.  
    The green points represent a subset of the normal late type galaxies (aimc 
    less than 25, excluding those with values of 1 or 2), and the blue contours 
    represents the remaining normal late type galaxies (aimc greater than 25).  
    It is clear that this morphological classification defines those galaxies 
    that are transitioning from the blue sequence to the red cloud.}
    \label{fig:NUVr_CMD}
\end{figure}

@@

% Histogram of NUV-r, with all, red, blue, green galaxies (aimc values)
\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/GV/NUVr_CMDclassifications}
    \caption[Distribution of NUV-$r$ of SDSS galaxies]{A histogram of the 
    NUV$-r$ color of those SDSS DR7 galaxies which are also detected in GALEX.  
    The red cloud, blue sequence, and green valley populations are separated by 
    the morphological types as defined by the KIAS-VAGC.  It is readily apparent 
    that the green valley galaxies exist in the space between the red cloud and 
    blue sequence.}
    \label{fig:NUVr_hist}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/GV/Mstar_hist}
    \caption[Stellar mass distribution by morphological type]{The distribution 
    of stellar mass for all galaxies in SDSS DR7, separated by their 
    morphological type.  The galaxies in the green valley have stellar masses 
    comparable to those in the red cloud.  The stellar masses of those galaxies 
    in the blue sequence range from the lowest mass objects up through the 
    stellar masses of the green valley galaxies.}
    \label{fig:M_hist}
\end{figure}

@@

Estimates of the gas-phase chemical abundances of galaxies probe their 
integrated star formation histories, which can provide insight into the 
enrichment of the ISM and CGM.  A few of the galaxies for which Douglass et al. 
(2017, submitted) are able to estimate metallicities reside in the green valley.  
When compared with the metallicities of galaxies in the blue sequence and red 
cloud, Fig. \ref{fig:Z_hist} shows that the green valley galaxies have higher 
nitrogen abundances than star-forming galaxies in the blue sequence (and some of 
the red cloud).  With oxygen abundances that fall within the same range as the 
other two galaxy populations, this shift causes the N/O ratio to be much higher 
in green valley galaxies than in the blue sequence.  Our interpretation of this 
shift is described in Sec. \ref{sec:discussion_GV}.

@@

\section[GV galaxy properties]{Understanding green valley galaxies}\label{sec:discussion_GV}

@@

Fig. \ref{fig:Mr_bin} shows a higher fraction of faint wall galaxies than faint 
void galaxies are in the green valley.  This would indicate that void galaxies 
are slightly behind wall galaxies in their evolution, matching predictions based 
on the $\Lambda$CDM cosmology.  These results also coincide with the 
observations of \cite{Douglass17b} and Douglass \& Vogeley (2017, submitted).  
They find that, for dwarf galaxies ($M_r > -17$), those which exist in voids may 
have commenced their star formation at a later time.  The higher fraction of 
wall dwarf galaxies in the green valley might also point to an environmental 
influence on the reason for transitioning through the green valley, such as ram 
pressure stripping, which would occur much less frequently in the void 
environment.  However, the existence of void galaxies in the green valley 
indicate that galaxy interactions cannot be the only star formation quenching 
mechanism.

@@

\section{Conclusions}

@@

There is a higher fraction of faint wall galaxies than faint void galaxies in 
the green valley.  In conjunction with the conclusions of \cite{Douglass17b} and 
Douglass et al. (2017, submitted), this indicates that void dwarf galaxies are 
less evolved than dwarf galaxies in denser environments.  It would be beneficial 
to investigate the small-scale ($\sim$1 \hMpc) environment of galaxies in the 
green valley, to determine if any interactions are responsible for the 
transitional state.

### 2017-06-17 KellyDouglass/Thesis/Thesis_sections/Paper1.tex
Added acknowledgments and dedication

\chapter[Metallicity of dwarf galaxies]{Determining the large-scale environmental dependence of gas-phase metallicity in dwarf galaxies}\label{ch:Paper1}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Theory]{Estimation of galaxy metallicity from optical spectroscopy}
\label{sec:Theory_P1}
% What is the physics?

@@

\begin{figure}
	\centering
    \includegraphics[width=0.5\textwidth]{Images/Paper1/energy_level_diagram-figure0}
	\caption[{[\ion{O}{3}] and [\ion{S}{2}] energy-level diagram}]{Energy-level 
	diagram for [O{\sc iii}] $(2p^2)$ and [S{\sc ii}] $(3p^3)$ ions.  The most 
	important transitions are shown; all are in the visible spectrum.  These 
	forbidden transitions in oxygen provide an estimate of the electron temperature 
	in the interstellar gas, while the forbidden sulfur transitions provide an 
	estimate of the electron number density.  With estimates of the electron 
	temperature and number density, we can convert emission line flux ratios into 
	chemical abundance ratios.}
	\label{fig:transitions_P1}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.5\textwidth]{Images/Paper1/1sig_I06_dwarf_SF_t3_OpOpp_Z12logOH}
    \caption[O$^+$/O$^{++}$ versus metallicity]{Metallicity of our 135 dwarf 
    galaxies as a function of O$^+$/O$^{++}$.  While either O$^+$ or O$^{++}$ 
    can dominate our galaxies' oxygen abundances, only those with low 
    metallicities (high temperatures) and with O$^+$ dominating the abundance 
    will be affected by the temperature overestimate of the low-ionization zone 
    as found by \cite{Andrews13}.  The small number of galaxies (15/135) that 
    may suffer from this possible temperature overestimate do not affect our 
    results.}
    \label{fig:O2O3_ratio}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Data]{SDSS data and galaxy selection}\label{sec:Data}
% What are the assumptions?
The SDSS Data Release 7 (DR7) \citep{Abazajian09} is a wide-field multi-band 
imaging and spectroscopic survey, using drift scanning to map approximately 
one-quarter of the northern sky.  Photometric data in the five band SDSS system 
--- $u$, $g$, $r$, $i$, and $z$ --- are taken with a dedicated 2.5-meter 
telescope at the Apache Point Observatory in New Mexico \citep{Fukugita96, 
Gunn98}.  Galaxies with a Petrosian $r$-band magnitude $m_r < 17.77$ are 
selected for spectroscopic analysis \citep{Lupton01, Strauss02}.  The spectra 
have an observed wavelength range of $3800\text{\AA}$ to $9200\text{\AA}$ with a 
resolution $\lambda / \Delta \lambda \sim 1800$, and are taken using two 
double fiber-fed spectrographs and fiber plug plates with a minimum fiber 
separation of 55 arcseconds \citep{Blanton03}.  The emission line flux data used 
in this study are from the MPA-JHU value-added catalog, which is based on the 
SDSS DR7 sample of galaxies.  Absolute magnitudes, colors, and all other 
additional data are from the KIAS value-added galaxy catalog \citep{Choi10}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Results]{Metallicity analysis and results}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper1/Yin07_comparison_fit}
    \caption[Metallicity comparison to \cite{Yin07}]{Metallicity (\OH) 
    comparison between our calculated estimates and those made by \cite{Yin07}.  
    Error bars have been omitted for clarity.  These are not the dwarf galaxies 
    analyzed in this paper, but rather the sample of galaxies analyzed by 
    \cite{Yin07} to confirm that our version of the calculation is correct.  
    Both \cite{Yin07} and we have used the metallicity method outlined by 
    \cite{Izotov06}.}
    \label{fig:Yin07_comp}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper1/1sig_dwarf_I06_SF_t3_T04comparison}
    \caption[Metallicity comparison to \cite{Tremonti04}]{Metallicity (\OH) 
    comparison between our calculated estimates and those made by 
    \cite{Tremonti04}.  Error bars have been omitted for clarity.  Excepting the 
    extreme low-metallicity galaxies we found, most galaxies agree reasonably 
    well with the values already published.  It is important to note that the 
    strong-line methods \citep[like those used by][]{Tremonti04} are not 
    calibrated for low-metallicity values and are known to overestimate the 
    metallicity by as much as 0.3 dex \citep{Kennicutt03}.  Thus, it is not 
    surprising that oxygen abundances measured using the direct method find 
    lower metallicity, particularly at very low metallicities.}
    \label{fig:T04comp}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper1/MZ_1sig_I06_dwarf_SF_t3_python}
    \caption[Stellar mass versus metallicity for 135 dwarf galaxy sample]
    {Stellar mass versus metallicity of the 135 analyzed dwarf galaxies.  Error 
    bars have been omitted for clarity.  Due to the limited range of mass (all 
    our galaxies are within a small range of masses, since we are looking only 
    at dwarf galaxies), we cannot derive our own relation between the mass and 
    metallicity.  Some previously published relations are plotted over our data 
    for comparison.  To place our sample in context, we have also included (grey 
    contours) those galaxies from the MPA-JHU catalog with metallicity estimates 
    by \cite{Tremonti04}.  It was from these galaxies that the published 
    relation of \cite{Tremonti04} was derived.}
    \label{fig:MZrelation}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{Images/Paper1/urHist_1sig_I06_dwarf_SF_t3}
    \caption[Color distribution of 135 dwarf galaxy sample compared to SDSS]{The 
    $u-r$ color distribution of our 135 dwarf galaxies (red/black histograms) as 
    compared to the color distribution of all SDSS dwarf galaxies as found in 
    Fig. 4 of \cite{Hoyle12} (red/blue curves).  It is clear that our galaxies 
    are among the bluest dwarf galaxies in SDSS.}
    \label{fig:colorHist}
\end{figure}

>>>>

\chapter[Metallicity of Dwarf Galaxies]{Determining the Large-Scale Environmental Dependence of GasPphase Metallicity in Dwarf Galaxies}\label{ch:Paper1}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Calculating metallicity]{Estimation of galaxy metallicity from optical spectroscopy}
\label{sec:Theory_P1}
% What is the physics?

@@

\begin{figure}
	\centering
    \includegraphics[width=0.75\textwidth]{Images/Paper1/energy_level_diagram-figure0}
	\caption[{[\ion{O}{3}] and [\ion{S}{2}] energy-level diagram}]{Energy-level 
	diagram for [O{\sc iii}] $(2p^2)$ and [S{\sc ii}] $(3p^3)$ ions.  The most 
	important transitions are shown; all are in the visible spectrum.  These 
	forbidden transitions in oxygen provide an estimate of the electron temperature 
	in the interstellar gas, while the forbidden sulfur transitions provide an 
	estimate of the electron number density.  With estimates of the electron 
	temperature and number density, we can convert emission line flux ratios into 
	chemical abundance ratios.}
	\label{fig:transitions_P1}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=0.75\textwidth]{Images/Paper1/1sig_I06_dwarf_SF_t3_OpOpp_Z12logOH}
    \caption[O$^+$/O$^{++}$ versus metallicity]{Metallicity of our 135 dwarf 
    galaxies as a function of O$^+$/O$^{++}$.  While either O$^+$ or O$^{++}$ 
    can dominate our galaxies' oxygen abundances, only those with low 
    metallicities (high temperatures) and with O$^+$ dominating the abundance 
    will be affected by the temperature overestimate of the low-ionization zone 
    as found by \cite{Andrews13}.  The small number of galaxies (15/135) that 
    may suffer from this possible temperature overestimate do not affect our 
    results.}
    \label{fig:O2O3_ratio}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[SDSS Data]{SDSS data and galaxy selection}\label{sec:Data}
% What are the assumptions?
The SDSS Data Release 7 (DR7) \citep{Abazajian09} is a wide-field multi-band 
imaging and spectroscopic survey, using drift scanning to map approximately 
one-quarter of the northern sky.  Photometric data in the five band SDSS system 
--- $u$, $g$, $r$, $i$, and $z$ --- are taken with a dedicated 2.5-meter 
telescope at the Apache Point Observatory in New Mexico \citep{Fukugita96, 
Gunn98}.  Galaxies with a Petrosian $r$-band magnitude $m_r < 17.77$ are 
selected for spectroscopic analysis \citep{Lupton01, Strauss02}.  The spectra 
have an observed wavelength range of $3800\text{\AA}$ to $9200\text{\AA}$ with a 
resolution $\lambda / \Delta \lambda \sim 1800$, and are taken using two 
double fiber-fed spectrographs and fiber plug plates with a minimum fiber 
separation of 55 arcseconds \citep{Blanton03}.  The emission line flux data used 
in this study are from the MPA-JHU value-added catalog, which is based on the 
SDSS DR7 sample of galaxies.  Absolute magnitudes, colors, and all other 
additional data are from the KIAS value-added galaxy catalog \citep{Choi10}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section[Analysis \& Results]{Metallicity analysis and results}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper1/Yin07_comparison_fit}
    \caption[Metallicity comparison to \cite{Yin07}]{Metallicity (\OH) 
    comparison between our calculated estimates and those made by \cite{Yin07}.  
    Error bars have been omitted for clarity.  These are not the dwarf galaxies 
    analyzed in this paper, but rather the sample of galaxies analyzed by 
    \cite{Yin07} to confirm that our version of the calculation is correct.  
    Both \cite{Yin07} and we have used the metallicity method outlined by 
    \cite{Izotov06}.}
    \label{fig:Yin07_comp}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper1/1sig_dwarf_I06_SF_t3_T04comparison}
    \caption[Metallicity comparison to \cite{Tremonti04}]{Metallicity (\OH) 
    comparison between our calculated estimates and those made by 
    \cite{Tremonti04}.  Error bars have been omitted for clarity.  Excepting the 
    extreme low-metallicity galaxies we found, most galaxies agree reasonably 
    well with the values already published.  It is important to note that the 
    strong-line methods \citep[like those used by][]{Tremonti04} are not 
    calibrated for low-metallicity values and are known to overestimate the 
    metallicity by as much as 0.3 dex \citep{Kennicutt03}.  Thus, it is not 
    surprising that oxygen abundances measured using the direct method find 
    lower metallicity, particularly at very low metallicities.}
    \label{fig:T04comp}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper1/MZ_1sig_I06_dwarf_SF_t3_python}
    \caption[Stellar mass versus metallicity for 135 dwarf galaxy sample]
    {Stellar mass versus metallicity of the 135 analyzed dwarf galaxies.  Error 
    bars have been omitted for clarity.  Due to the limited range of mass (all 
    our galaxies are within a small range of masses, since we are looking only 
    at dwarf galaxies), we cannot derive our own relation between the mass and 
    metallicity.  Some previously published relations are plotted over our data 
    for comparison.  To place our sample in context, we have also included (grey 
    contours) those galaxies from the MPA-JHU catalog with metallicity estimates 
    by \cite{Tremonti04}.  It was from these galaxies that the published 
    relation of \cite{Tremonti04} was derived.}
    \label{fig:MZrelation}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{Images/Paper1/urHist_1sig_I06_dwarf_SF_t3}
    \caption[Color distribution of 135 dwarf galaxy sample compared to SDSS]{The 
    $u-r$ color distribution of our 135 dwarf galaxies (red/black histograms) as 
    compared to the color distribution of all SDSS dwarf galaxies as found in 
    Fig. 4 of \cite{Hoyle12} (red/blue curves).  It is clear that our galaxies 
    are among the bluest dwarf galaxies in SDSS.}
    \label{fig:colorHist}
\end{figure}
